Attribution of undesirable character traits, rather than trait-based dehumanization, predicts punishment decisions

### 2024-07-03 manuscript.Rmd
Update manuscript.Rmd

---
title: "Attribution of undesirable character traits, rather than trait-based dehumanization, predicts punishment decisions"
author: "Robert A. Brennan$^1$, Florence E. Enock$^{1,2}$, & Harriet Over$^1$"
output:
   bookdown::pdf_document2:
    keep_tex: true
    toc: false
    fig_caption: yes
header-includes:
  # - \usepackage{setspace}\doublespacing
  - \usepackage{caption}
bibliography: references.bib
link-citations: true
linkcolor: black
csl: apa-6th-edition.csl
---

>>>>

---
title: "Attribution of undesirable character traits, rather than trait-based dehumanization, predicts punishment decisions"
author: "Robert A. Brennan$^1$, Florence E. Enock$^{1,2}$, & Harriet Over$^1$"
output:
   bookdown::pdf_document2:
    keep_tex: true
    toc: false
    fig_caption: yes
header-includes:
  # - \usepackage{setspace}\doublespacing
  - \usepackage{caption}
bibliography: references.bib
link-citations: true
linkcolor: black
csl: apa-7th-edition.csl
---
